---
title: "Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# SimpLin

This package contains two functions, SimpLinR and SimpLinCpp. SimpLinCpp is an Rcpp function and SimpLinR is an R function.

## SimpLinCpp.cpp

SimpLinCpp takes two numeric vectors as inputs and fits a simple linear regression model. It returns a list containing estimated regression coefficients, standard errors, 95% confidence intervals, residuals, and fitted values. We will demonstrate how to call the function.

```{r}
library(SimpLin)

# Create numeric vectors for inputs
x = runif(100)
y = 2*x + runif(100)

# Call SimpLinCpp
outputList = SimpLinCpp(x, y)
```

## SimpLinR.R

SimpLinR is a wrapper function for SimpLinCpp and throws an error if either of the two inputs are not numeric vectors. We will demonstrate how to call the function.

```{r}
library(SimpLin)

# Create numeric vectors for inputs
x = runif(100)
y = 2*x + runif(100)

# Call SimpLinR
outputList = SimpLinR(x, y)

# Inputs other than numeric vectors
#SimpLinR(c("a", "b", "c"), y)
```
