---
title: "Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: sentence
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# SimpLin

This package contains functions that fit a simple linear regression model for a given predictor and response variable.
We will show use cases for each function and describe the output of the function.

## SimpLinCpp.cpp

SimpLinCpp takes two numeric vectors as inputs and fits a simple linear regression model.It returns a list containing the following:

-   **coefficients**: a vector of estimated regression coefficients, $\hat\beta_0$ and $\hat\beta_1$ respectively.

-   **se**: a vector of standard errors associated with $\hat\beta_0$ and $\hat\beta_1$ respectively.

-   **CI_upper**: a vector of upper bounds for the 95% confidence interval associated with $\hat\beta_0$ and $\hat\beta_1$ respectively.

-   **CI_lower**: a vector of lower bounds for the 95% confidence interval associated with $\hat\beta_0$ and $\hat\beta_1$ respectively.

-   **Residuals**: a vector of residuals defined as $y - \hat{y}$.

-   **Fitted_Values**: a vector of fitted values from the model.

```{r}
library(SimpLin)

# Create numeric vectors for inputs
x = runif(10)
y = 2*x + runif(10)

# Call SimpLinCpp
outputList = SimpLinCpp(x, y)
```

## SimpLinR.R

SimpLinR is a wrapper function for SimpLinCpp and throws an error if either of the two inputs are not numeric vectors.
It returns a list containing the following:

-   **coefficients**: a vector of estimated regression coefficients, $\hat\beta_0$ and $\hat\beta_1$ respectively.

-   **se**: a vector of standard errors associated with $\hat\beta_0$ and $\hat\beta_1$ respectively.

-   **CI_upper**: a vector of upper bounds for the 95% confidence interval associated with $\hat\beta_0$ and $\hat\beta_1$ respectively.

-   **CI_lower**: a vector of lower bounds for the 95% confidence interval associated with $\hat\beta_0$ and $\hat\beta_1$ respectively.

-   **Residuals**: a vector of residuals defined as $y - \hat{y}$.

-   **Fitted_Values**: a vector of fitted values from the model.

```{r}
library(SimpLin)

# Create numeric vectors for inputs
x = runif(100)
y = 2*x + runif(100)

# Call SimpLinR
outputList = SimpLinR(x, y)
```
